Leadership across 59 traditional cultures: an exploratory analysis

### 2019-12-03 leadership_across_cultures_contexts.Rmd
Provided coding example

For additional details on ethnographic sampling and creation of the *leadershipdata* package see @garfield_evolutionary_2019.

@@

Leadership in residential subgroups (e.g., hunting party, work group) was relatively common among hunter-gatherers but relatively rare among agriculturists. Leadership at the surpacommunity level, in contrast, was relatively rare among hunter-gatherers but quite common among agriculturists. The only example of supracommunity leadership among hunter-gatherers was from the Andamanese, a group of populations of Negrito hunter-gatherers of the Andaman Islands  by @az02-001: p. 45, who discussed the roles of a "head chief" from a permanent residential location and their marginal influence over other, local residential leaders:

>Their domestic policy may be described as a communism modified by the authority, more or less nominal, of the chief. The head chief of a tribe is called maia igla and the elders, or sub-chiefs, i.e. those in authority over each community, consisting of from 20 to 50 individuals, maicla . The head chief, who usually resides at a permanent encampment, has authority over all the sub-chiefs, but his power, like theirs, is very limited. It is exercised mainly in organising meetings between the various communities belonging to his tribe, and in exerting influence in all questions affecting the welfare of his followers. It is the chief alone, as may be supposed, who directs the movements of a party while on hunting and fishing expeditions, or when migrating. It is usually through his intervention that disputes are settled, but he possesses no power to punish or enforce obedience to his wishes, it being left to all alike to take the law into their own hands when aggrieved. The aryoto and eremtaga in each tribe have their own head chief, who are independent the one of the other.

>>>>

We illustrate our coding with an example from Andamanese hunter-gatherers [@az02-001, p. 45]:

>Their domestic policy may be described as a communism modified by the authority, more or less nominal, of the chief. The head chief of a tribe is called maia igla and the elders, or sub-chiefs, i.e. those in authority over each community, consisting of from 20 to 50 individuals, maicla. The head chief, who usually resides at a permanent encampment, has authority over all the sub-chiefs, but his power, like theirs, is very limited. It is exercised mainly in organising meetings between the various communities belonging to his tribe, and in exerting influence in all questions affecting the welfare of his followers. It is the chief alone, as may be supposed, who directs the movements of a party while on hunting and fishing expeditions, or when migrating. It is usually through his intervention that disputes are settled, but he possesses no power to punish or enforce obedience to his wishes, it being left to all alike to take the law into their own hands when aggrieved. The aryoto and eremtaga in each tribe have their own head chief, who are independent the one of the other.

This text record was coded has having evidence for the functions *Resolve conflict*, *Organize cooperation*, *Movement/migration*, *Provide subsistence*, and *Misc. social functions*. For qualities, there was evidence for *High status*. Although authority is mentioned, we did not code evidence for this variable because the chief "possesses no power to punish or enforce obedience to his wishes," contrary to our operationalization. For additional details on ethnographic sampling and creation of the *leadershipdata* package see @garfield_evolutionary_2019.

@@

Leadership in residential subgroups (e.g., hunting party, work group) was relatively common among hunter-gatherers but relatively rare among agriculturists. Leadership at the surpacommunity level, in contrast, was relatively rare among hunter-gatherers but quite common among agriculturists. The only example of supracommunity leadership among hunter-gatherers was from the Andamanese, a group of populations of Negrito hunter-gatherers of the Andaman Islands by [@az02-001, p. 45], who discussed the roles of a "head chief" from a permanent residential location and their marginal influence over other, local residential leaders (see quote in Methods section).
